### 2023-09-01 paper/FPF-WG1.tex
some polishing
Update FPF-WG1.tex

@@

Proton-proton collisions at the LHC produce an intense collimated beam of high-energy (TeV) neutrinos
in the forward direction.
%
The recent  observation of LHC neutrinos by the FASER$\nu$ and SND@LHC experiments
indicates that this hitherto ignored beam becomes available for scientific investigations.
%
Neutrino deep-inelastic scattering (DIS) is known
to provide a sensitive probe of the quark flavour separation in nucleons
and nuclei.
%
Here we quantify the projected impact of DIS neutrino structure functions at the LHC
on the parton distribution functions (PDFs) of protons and heavy nuclei.
%
We generate differential structure function DIS pseudo-data 
for  FASER$\nu$ and SND@LHC based on the Run III luminosity,
as well as for the FASER$\nu$2, AdvSND, and FLArE experiments
to be  hosted at the proposed
 Forward Physics Facility (FPF) operating concurrently with the High Luminosity LHC.
 %
 By using both the Hessian profiling of PDF4LHC21 with {\sc\small xFitter} and
 the  NNPDF open-source framework,
 we highlight the impact on the proton and nuclear PDFs of the FPF
 experiments in a kinematic region in $x$ and $Q^2$ comparable to that
 covered by the upcoming
 Electron-Ion Collider (EIC).
 %
 This sensitivity is found to be the largest for  strangeness as well as for
 the up and down valence quark PDFs, and lead to improved theoretical
 predictions for key scattering processes at the HL-LHC.
%
 Our analysis demonstrates how exploiting the potential
 of this unique LHC neutrino beam  effectively
extends the CERN infrastructure with a ``Neutrino-Ion Collider''.

@@

% Introduction and motivation
\input{sec-introduction}

% Generation of FPF DIS structure functions pseudo-data
\input{sec-dis-pseudodata}

% REsults 
\input{sec-results}

% Pheno
\input{sec-pheno}

% Summary and outlook
\input{sec-summary}

% Appendices
\appendix

% Impact of FASERnu
\input{app-faser.tex}

% Impact in nuclear PDFs
\input{app-nuclearPDFs.tex}

>>>>

\vspace{-2.0cm}
\begin{flushright}
Nikhef-2023-aaa\\
\end{flushright}
\vspace{0.6cm}

@@

Proton-proton collisions at the LHC generate a high-intensity collimated beam of neutrinos
in the forward (beam) direction, characterised by energies of up to several TeV.
%
The recent  observation of LHC neutrinos by FASER$\nu$ and SND@LHC
signals that this hitherto ignored particle beam is now available for scientific inquiry.
%
Here we quantify the impact that neutrino deep-inelastic scattering (DIS) structure function
measurements at the LHC would have
on the parton distributions (PDFs) of protons and heavy nuclei.
%
We generate projections for DIS structure functions
at FASER$\nu$ and SND@LHC,
as well as at the FASER$\nu$2, AdvSND, and FLArE experiments
to be  hosted at the proposed
Forward Physics Facility (FPF) operating concurrently with the High-Luminosity LHC.
%
These measurements are found to cover a kinematic region in $x$ and $Q^2$ comparable to that
of the upcoming Electron-Ion Collider, with sub-percent statistical uncertainties
in the FPF case.
%
Including these DIS projections into global (n)PDF analyses, specifically PDF4LHC21, NNPDF4.0,
 and EPPS21,  reveals a significant reduction of PDF uncertainties, in particular
 for strangeness and the up and down valence PDFs.
 %
 We demonstrate that LHC neutrino data enables improved theoretical
 predictions for core processes at the HL-LHC, such as Higgs and weak gauge (di)boson production.
%
 Our analysis highlights how exploiting the LHC neutrino beam effectively
provides CERN with a new ``Neutrino-Ion Collider''.

@@

\input{sec-introduction}
\input{sec-dis-pseudodata}
\input{sec-results}
\input{sec-pheno}
\input{sec-summary}

\appendix
\input{app-faser.tex}
\input{app-nuclearPDFs.tex}
